 Austral Spring Extratropical Southern Hemisphere zonally assymetric circulation

### 2021-07-26 analysis/paper/shceof.Rmd
🙄 "En la sección métodos están los médotos..."

\textcolor{red}{The data and methods are described in Section 2 :P ...}

# Data and Methods

@@

## cEOF spatial patterns

@@

## cEOFs Regressions

@@

## cEOFs relationship with other variables

@@

## Tropical sources

@@

## Precipitation

>>>>

In Section \@ref(methods) we describe the methods.
In Section \@ref(temporal) we describe the temporal variability and vertical coherence of the indices.
In Section \@ref(spatial), we analyse the spatial patterns of each complex EOF.
In Section \@ref(regressions) we study the spatial regressions with geopotential height and temperatuer. 
In Section \@ref(other-variables), we analyise the relationship between cEOF1 and Ozone, and between EOF2 and the Southern Annular Mode and the PSA. 
In Section \@ref(tropical) we look for tropical forcings that explain the variability of each cEOF. 
Finally, in Section \@ref(precipitation) we show the relationship between these modes of variabiltiy and precipitation in South America and Oceania.

# Data and Methods {#methods}

@@

## cEOF spatial patterns {#spatial}

@@

## cEOFs Regressions {#regressions}

@@

## cEOFs relationship with other variables {#other-variables}

@@

## Tropical sources  {#tropical}

@@

## Precipitation {#precipitation}
